# Data Frame excercises

## 1. Write a R program to create an empty data frame.
```{r}
df <- data.frame()
df
```
or like this
```{r}
df2 = data.frame(Ints = integer(),
                Doubles = double(),
                Characters = character(),
                Logicals = logical(),
                Factors = factor(),
                stringsAsFactors = FALSE)
print("Structure of the empty dataframe:")
print(str(df))
```

## 2. Write a R program to create a data frame from four given vectors.

```{r}
vector_1 <- c(1:3)
vector_2 <- c("a", "b", "c")
vector_3 <- c(TRUE, FALSE, TRUE)
vector_4 <- c(rnorm(3))
df <- data.frame(index = vector_1,
                 char = vector_2,
                 bool = vector_3,
                 rnd = vector_4)
df
```
more data:
```{r}
name = c('Anastasia', 'Dima', 'Katherine', 'James', 'Emily', 'Michael', 'Matthew', 'Laura', 'Kevin', 'Jonas')
score = c(12.5, 9, 16.5, 12, 9, 20, 14.5, 13.5, 8, 19)
attempts = c(1, 3, 2, 3, 2, 3, 1, 1, 2, 1)
qualify = c('yes', 'no', 'yes', 'no', 'no', 'yes', 'yes', 'no', 'no', 'yes')
df_students = data.frame(name, score, attempts, qualify)
df_students
```

## 3. Write a R program to get the structure of a given data frame.

```{r}
str(df)
```
```{r}
str(df_students)
```

## 4. Write a R program to get the statistical summary and nature of the data of a given data frame.

```{r}
summary(df)
# column summary
summary(df$bool)
```

## 5. Write a R program to extract specific column from a data frame using column name.

```{r}
column_bool <- data.frame(df$bool)
column_bool
# two cols
df_cols_2 <- data.frame(df$index, df$char)
df_cols_2
```

## 6. Write a R program to extract first two rows from a given data frame.

```{r}
two_rows <- df[1:2,] 
two_rows
```


## 7. Write a R program to extract 3rd and 5th rows with 1st and 3rd columns from a given data frame.
 
```{r}
rows_cols <- df_students[c(3, 5), c(1, 3)]
rows_cols
```

## 8. Write a R program to add a new column in a given data frame.

```{r}
grade <- numeric()
df_students["grade"] <- grade
df_students
```
Or in other way:

```{r}
df_students$country <- c(rep("UK", 10))
df_students
```


## 9. Write a R program to add new row(s) to an existing data frame.

It's a strange way, but it works
```{r}
df_students[(nrow(df_students) + 1),] <- c("Name", 20.1, 1, "yes", NA, "UK")
df_students
```
Another way:
```{r}
new_exam_data = data.frame(
name = c('Robert', 'Sophia'),
score = c(10.5, 9),
attempts = c(1, 3),
qualify = c('yes', 'no'),
grade = c(NA, NA),
country = c("UK", "UK")
)
df_students =  rbind(df_students, new_exam_data)
df_students
```

## 10. Write a R program to drop column(s) by name from a given data frame.
 
```{r}

```


## 11. Write a R program to drop row(s) by number from a given data frame.
 
```{r}

```


## 12. Write a R program to sort a given data frame by multiple column(s).
 

## 13. Write a R program to create inner, outer, left, right join(merge) from given two data frames.
 

## 14. Write a R program to replace NA values with 3 in a given data frame.
 

## 15. Write a R program to change a column name of a given data frame.
 

## 16. Write a R program to change more than one column name of a given data frame.
 

## 17. Write a R program to select some random rows from a given data frame.
 

## 18. Write a R program to reorder an given data frame by column name.
 

## 19. Write a R program to compare two data frames to find the row(s) in first data frame that are not present in second data frame.
 

## 20. Write a R program to find elements which are present in two given data frames.
 

## 21. Write a R program to find elements come only once that are common to both given data frames.
 

## 22. Write a R program to save the information of a data frame in a file and display the information of the file.
 

## 23. Write a R program to count the number of NA values in a data frame column.
 

## 24. Write a R program to create a data frame using two given vectors and display the duplicated elements and unique rows of the said data frame.
 

## 25. Write a R program to call the (built-in) dataset airquality. Check whether it is a data frame or not? Order the entire data frame by the first and second column.
 

## 26. Write a R program to call the (built-in) dataset airquality. Remove the variables 'Solar.R' and 'Wind' and display the data frame.